Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-01-16 RR_manuscript/Draft_RR.Rmd
:construction: - move figure to figs/ (WIP)
update fig error

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

```{r forkingPaths, echo=FALSE, fig.cap="Illustrations of the analytical flexibility associated with acoustic analyses. (A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b. The words \"another is highlighted by the green box\"; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch", fig.dim = c(6, 2)}

knitr::include_graphics("./RR_manuscript/img/ForkingPaths.png")

>>>>

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

In text ref to Figure \@ref(fig:forkingPaths)

(ref:forkingPaths) Illustrations of the analytical flexibility associated with acoustic analyses. (A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b. The words ``another is highlighted by the green box''; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.

```{r 'forkingPaths', echo=FALSE, fig.cap="(ref:forkingPaths)", out.width="100%"}

knitr::include_graphics(here::here("figs", "ForkingPaths.png"))
